% !TEX encoding = UTF-8 Unicode
% !TEX root = ../curriculum.tex

\cvsection{Experience}

\begin{cventries}
	
%---------------------------------------------------------
\cventry
{Python Developer} % Job title
{Sunai} % Organization
{Santiago, Chile} % Location
{DEC 2022 - JUN 2023} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Automatic data loading into ETL system for API and FTP.}
		\item {Design and creation of tables, queries and procedures in PostgreSQL.}
		\item {Integration of Python code with GCP (GMail, Drive and Sheets).}
		\item {Automatic data loading to AWS Buckets.}
		\item {Process improvements and creation of in-house automation tools.}
        \item {Test-driven development (TDD) with pytest and coverage.}
		\item {Setting up Pipelines on Bitbucket.}
		\item {Automated report generation with PostgreSQL, C\# and LaTeX under CLEAN architecture.}
        \item {Data loading and validation from local XLSX files.}
		\item {Creation of Bash scripts for Jenkins procedures.}
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Freelance Developer} % Job title
    {Estudio 6/8} % Organization
    {Santiago, Chile} % Location
    {MAR 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical and creative director of the Bakumapu (RPG) videogame.}
        \item {Neovim plugins development (Lua):
          \href{https://github.com/polirritmico/telescope-lazy-plugins.nvim}{Telescope Lazy Plugins},
          \href{https://github.com/polirritmico/monokai-nightasty.nvim}{Monokai Nightasty}},
          \href{https://github.com/polirritmico/lazy-local-patcher.nvim}{Lazy Local Patcher},
          \href{https://github.com/polirritmico/simple-boolean-toggle.nvim}{Simple Boolean Toggle}.
        \item {Programming in GDScript under the open-source Godot engine.}
        \item {Programming in Python and PyQT libraries for internal development tools.}
        \item {Design of work methodologies and organization using Kanban on Trello and GitHub platforms.}
        \item {Development using TDD and CI/CD.}
        \item {LaTeX documentation automatically converted to HTML.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {FONDECYT N.° 3210600} % Organization
    {Santiago, Chile} % Location
    {AUG 2021 - DEC 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database creation and web research.}
        \item {Python programming, RegEx searches and web scraping tool.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Digital Literacy Course Instructor} % Job title
    {Innovacien NGO} % Organization
    {Rancagua, Chile} % Location
    {NOV 2021 - DEC 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted courses on basic Windows usage, Microsoft Office and web browsing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Woodworker} % Job title
    {Making and designing of furniture and controllers} % Organization
    {Santiago, Chile} % Location
    {JAN 2018 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation of low-latency MIDI controllers with Arduino (C, C++).}
        \item {Furniture design and 3D modeling in SketchUp.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Musician, Composer, Luthier and Performer}
    {La Recogida Theater Company}
    {Santiago, Chile}
    {JUL 2012 - DEC 2014}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of wireless MIDI controller for real-time sample and effects.}
        \item {Bluetooth pedal controller for sheet music display.}
      \end{cvitems}
    }   

%---------------------------------------------------------
  \cventry
    {Drummer and Percussionist}
    {Various Orchestras, Bands and Ensembles}
    {Santiago, Chile}
    {ENE 2005 - present}
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    	  \item {MIDI synchronization systems via LAN between Ableton Live and Resolume Arena for real-time visuals and audio SFX.}
    	  \item {MIDI programming and MAX plugins.}
        \item {Percussionist in OFU, OSJN, IMUC Percussion Ensemble, UC Pastoral Musicals.}
        \item {Independent projects and various bands of popular and experimental music.}
      \end{cvitems}
		}

%---------------------------------------------------------
  \cventry
    {Music Teacher} % Job title
    {Various Schools} % Organization
    {Santiago, Chile} % Location
    {APR 2015 - DEC 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SS. CC. Manquehue School (2015-2019).}
        \item {Altamira School (2018).}
        \item {Esperanza Educational Complex (2016).}
      \end{cvitems}
    }

\end{cventries}

